\section{Nonfunctional Requirements}
\begin{enumerate}
    \item Performance Requirements
    \begin{itemize}
        \item The system should respond to user requests within \textbf{2 seconds} under normal load.
        \item It should support at least \textbf{1000 concurrent users} without performance degradation.
        \item Database queries should be optimized to execute within \textbf{500 milliseconds} on average.
        \item The system should be able to handle a \textbf{10,000-record dataset} efficiently.
    \end{itemize}

    \item Security Requirements
    \begin{itemize}
        \item User authentication should be enforced using \textbf{OAuth 2.0 or JWT-based authentication}.
        \item Institutional email verification should be required for teacher and admin accounts.
        \item Passwords should be \textbf{hashed and stored securely} using bcrypt or Argon2.
        \item The system should prevent \textbf{SQL injection, cross-site scripting (XSS), and cross-site request forgery (CSRF)}.
        \item Role-based access control (RBAC) should be implemented to restrict access to different sections of the system.
    \end{itemize}

    \item Usability Requirements
    \begin{itemize}
        \item The user interface should be \textbf{intuitive and accessible} to users of different technical backgrounds.
        \item The system should follow \textbf{WCAG 2.1 Level AA} accessibility standards.
        \item Mobile responsiveness should be ensured across devices with different screen sizes.
        \item The system should support \textbf{Bengali and English languages}.
    \end{itemize}

    \item Availability Requirements
    \begin{itemize}
        \item The system should have \textbf{99.5\% uptime} except for planned maintenance.
        \item In case of a failure, the system should be \textbf{recoverable within 30 minutes}.
        \item Automated database backups should be scheduled \textbf{daily} and retained for at least \textbf{30 days}.
    \end{itemize}

    \item Maintainability and Scalability
    \begin{itemize}
        \item The system should follow a \textbf{modular architecture} for easy maintenance and updates.
        \item The backend should be designed using \textbf{RESTful API principles}, and \textbf{Software Design Best Practices and Patterns}.
        \item The system should be \textbf{horizontally scalable} to accommodate an increase in users.
        \item The system should be \textbf{vertically scalable} to accommodate an increase in data (such as, resources) volume.
        \item Logging and monitoring should be implemented using \textbf{ELK stack or Prometheus}.
    \end{itemize}

    \item Data Integrity and Consistency
    \begin{itemize}
        \item The database should maintain \textbf{ACID compliance} for transactions.
        \item The system should ensure that \textbf{no duplicate user accounts} are created.
        \item All updates to the database should follow \textbf{proper validation and constraints}.
    \end{itemize}

    \item Compatibility Requirements
    \begin{itemize}
        \item The frontend should be \textbf{compatible with modern browsers} (Chrome, Firefox, Edge, Safari).
        \item The backend should be deployable on \textbf{Linux-based cloud servers}.
        \item The database should support either \textbf{SQL-based relational models (PostgreSQL/MySQL/SQLite)} or \textbf{no SQL models (MongoDB/Redis)}.
    \end{itemize}

    \item Logging and Monitoring
    \begin{itemize}
        \item All system events should be \textbf{logged with timestamps and user activity}.
        \item Error logs should be stored and categorized based on severity.
        \item A monitoring dashboard should be available for \textbf{system health checks}.
    \end{itemize}

    \item Disaster Recovery and Backup
    \begin{itemize}
        \item The system should have a \textbf{disaster recovery plan} to restore services quickly.
        \item Backups should be \textbf{stored in a separate location} to avoid single-point failure.
        \item Regular \textbf{testing of backup restoration} should be performed.
    \end{itemize}
\end{enumerate}